%-------------------------
% Resume in Latex
% template Author : Sidratul Muntaha Ahmed
% template License : MIT

% Myself : Liu Zhe You
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Jason(Zhe-You) Liu} \\ \vspace{1pt}
    \small \href{mailto:jasonliu@apache.org}{\underline{jasonliu@apache.org}} $|$ 
    \href{https://github.com/jason810496}{\underline{GitHub}} $|$
    \href{https://www.linkedin.com/in/zhe-you-liu/}{\underline{LinkedIn}} $|$
    \href{https://blog.zhu424.dev/}{\underline{Blog}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \resumeItemListStart
    \resumeItem{\textbf{Open Source Experience}: \href{https://github.com/apache/airflow/pulls?q=is\%3Apr+author\%3Ajason810496+is\%3Amerged}{\textcolor{blue}{\underline{Contributed 100+ PRs}}} and \href{https://github.com/apache/airflow/pulls?q=is\%3Apr+reviewed-by\%3Ajason810496+}{\textcolor{blue}{\underline{reviewed 300+}}} with detailed feedback in \textbf{Apache Airflow}. Collaborated with engineers from \textbf{AWS}, \textbf{GCP}, \textbf{Astronomer}, etc. Invited as \href{https://lists.apache.org/thread/lrjgl630mdhvzmpdt5tvp425kpqkrl8m}{\textcolor{blue}{\underline{Committer}}} within 5 months.}
    \resumeItem{\textbf{Backend Engineer} with \textbf{3+ years} of SDLC across \textbf{4 companies}, including \textbf{Microsoft}, \textbf{Appier}, etc.}
    \resumeItem{\textbf{Conference Speaker} at multiple \textbf{international events}, including \href{https://communityovercode.org/past-sessions/community-over-code-na-2025/}{\textcolor{blue}{\underline{ApacheCon NA}}}, \href{https://airflowsummit.org/sessions/2025/becoming-an-apache-airflow-committer-from-0/}{\textcolor{blue}{\underline{Airflow Summit}}}, etc.}
    \resumeItem{\textbf{ICPC} Asia Taiwan Regional \href{https://www.linkedin.com/in/zhe-you-liu/overlay/1635552153532/single-media-viewer/?profileId=ACoAADypogYB37Bb3cfyiwt5RnsZYRtLPFnOo-k}{\textcolor{blue}{\underline{Bronze Medalist}}}.}
  \resumeItemListEnd

% resumeItem SHOULD SHORTER THAN 115 characters

%-----------OPEN SOURCE CONTRIBUTIONS-----------
\section{Open Source Contributions}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Apache Airflow $|$ Committer}{October 2024 - Present}
      {A data orchestration tool with over 40k stars on GitHub, used by more than 70,000 companies.}{}
      \resumeItemListStart
        % \resumeItem{Invited as \href{https://lists.apache.org/thread/lrjgl630mdhvzmpdt5tvp425kpqkrl8m}{\textcolor{blue}{\underline{Apache Airflow Committer}}} in 5 month during semester.}
        % \resumeItem{\href{https://github.com/apache/airflow/pulls?q=is\%3Apr+author\%3Ajason810496+is\%3Amerged}{\textcolor{blue}{\underline{Contributed 100+ PRs}}} and \href{https://github.com/apache/airflow/pulls?q=is\%3Apr+reviewed-by\%3Ajason810496+}{\textcolor{blue}{\underline{reviewed 200+}}} with feedback in the past year.}
        \resumeItem{\href{https://github.com/apache/airflow/pull/49470}{\textcolor{blue}{\underline{Fixed OOM issue when reading large logs in the API Server}}}, \textbf{reducing memory usage by 10x}.}
        \resumeItem{Refactored the parameter system and database exception handling, \textbf{benefiting over 50 API endpoints}.}
        \resumeItem{\textbf{Led} and developed the \href{https://github.com/apache/airflow/issues/42360}{\textcolor{blue}{\underline{authentication and authorization system}}} for the core API, enhancing security.}
        \resumeItem{Fixed \href{https://github.com/apache/airflow/pulls?q=\%3Apr+author\%3Ajason810496+is\%3Amerged+Fix+k8s+}{\textcolor{blue}{\underline{five Kubernetes flaky system tests}}} by adding exponential retries in critical sections, improving CI stability.}
        \resumeItem{\textbf{Initiated} the development for supporting \href{https://github.com/apache/airflow/issues/52712}{\textcolor{blue}{\underline{providers of Event-Driven Scheduling}}}, \textbf{one of the 3.0 core features}.}
      \resumeItemListEnd

    \resumeSubheading
      {LFX Mentorship – CNCF Krkn $|$ Mentee}{May 2025 – August 2025}
      {Krkn is a CNCF sandbox project focused on chaos and resiliency testing.}{}
      \resumeItemListStart
        \resumeItem{Selected as a mentee for \href{https://mentorship.lfx.linuxfoundation.org/project/92e42a9c-fc0a-46bf-8ca7-69ad673dcce0}{\textcolor{blue}{\underline{LFX Mentorship}}}; collaborating with Red Hat engineers to develop the feature.}
        \resumeItem{Designed a robust \href{https://docs.google.com/document/d/11KwSi\_c\_WkkD6I2jbBEMQR-GEjIqOVVu0fviBVQ-9cQ}{\textcolor{blue}{\underline{proposal}}} for a \href{https://github.com/cncf/mentoring/blob/main/programs/lfx-mentorship/2025/02-Jun-Aug/README.md\#chaos-scenario-rollback-feature}{\textcolor{blue}{\underline{rollback scenarios feature}}}, which received \href{https://www.linkedin.com/posts/activity-7368293254267551746-xlVd?utm_source=share&utm_medium=member_desktop\&rcm=ACoAADypogYB37Bb3cfyiwt5RnsZYRtLPFnOo-k}{\textcolor{blue}{\underline{positive feedback}}} from the team.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Appier $|$ Backend Intern at Data Platform Department}{July 2024 – September 2025}
    {\emph{Distributed System, Data Ingestion, Airflow, Databricks, Kubernetes, Terraform}}{Hybrid Working}
    \resumeItemListStart
        \resumeItem{Built a centralized config onboarding service with Airflow, powering pipelines across 6 core features.}
        \resumeItem{Refactored a data ingestion API from Flask to FastAPI, migrating 50K+ lines from Hive to Delta Lake.}
        \resumeItem{Created an integration testing framework with auto API docs, cutting dev time by over 50\%.}
        \resumeItem{Developed a shared API client generator for internal metadata API used by 5+ services.}    
        \resumeItem{Developed an operations dashboard integrated with OAuth, RBAC and k8s API, supporting usage across 5 teams. }
    \resumeItemListEnd
  \resumeSubheading
    {PAIA $|$ Part-time Backend}{December 2023 – July 2024}
    {\emph{Django, PostgreSQL, Redis, Docker, Pytest, Performance Profiling}}{Hybrid Working}
    \resumeItemListStart
        \resumeItem{Fix the Redis anti-pattern for calculating `today\_login\_count` and speed it up over 300 times.}
        \resumeItem{Developing new features and refactoring with Test-Driven Development.}
    \resumeItemListEnd
  % \resumeSubheading
  %   {GLSoft $|$ Part-time Software Engineer}{April 2023 – March 2024}
  %   {\emph{B2B digital transformation company; solution research, building PoC, API testing.}}{Hybrid Working} 
     
    \resumeSubHeadingListEnd


%-----------COMMUNITY AND LEADERSHIP-----------
\section{Community \& Leadership}
  \resumeSubHeadingListStart

    \resumeSubheading
      {OpenSource4You apache-airflow $|$ Mentor}{March 2025 – Present}
      {\href{https://github.com/opensource4you/readme}{\textcolor{blue}{\underline{OpenSource4You}}} is a Mandarin-based community actively contributing to large-scale OSS.}{}
      \resumeItemListStart
        \resumeItem{Assist new contributors with onboarding, answering questions, and guidance.}
      \resumeItemListEnd

    \resumeSubheading
      {Apache CommunityOverCode(ApacheCon) North America 2025, Airflow Summit 2025$|$ Speaker}{}
      {Topic : “Becoming an Apache Airflow Committer from 0“ \href{https://speakerdeck.com/zhu424/apache-communityovercode-na-2025-becoming-an-apache-airflow-committer-from-0}{\textcolor{blue}{\underline{[1]}}} \href{https://speakerdeck.com/zhu424/airflow-submit-2025-becoming-an-apache-airflow-committer-from-0}{\textcolor{blue}{\underline{[2]}}}}{}

    \resumeSubheading
      {MOPCON(Mobile Open Platform Conference) $|$ Speaker}{November 2023}
      {Topic : “Creating an AI training ROS map editor using Three.js, exporting to FBX for use in Unity.”}{\href{https://youtu.be/nbhyWtfXoc8?si=SoeKS7mpijNQ03L3\&t=1460}{\textcolor{blue}{\underline{Youtube link}}}}

    % \resumeSubheading
    %   {Wuling Computer Science Club $|$ Director \& DSA Lecturer}{July 2020 – July 2021}
    %   {Increasing course engagement by 30\% by leading committee members to organize diverse lectures.}{}

    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Cheng Kung University}{Tainan , TW}
      {Bachelor of Computer Science and Information Engineering}{Expected June 2026}
          \resumeItemListStart
          \resumeItem{\textbf{TSMC Hackathon - IT Infra Automation Monitoring using GenAI 2024} :} Second Place
            \resumeItem{\textbf{ICPC Asia Taiwan Regional Programming Contest 2023} :} Bronze Medal
            % \resumeItem{\textbf{National Collegiate Programming Contest 2023 \& 2022} :} Merit Award
          \resumeItemListEnd

  \resumeSubHeadingListEnd

% %-----------PROJECTS-----------
% \section{Projects}

%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%       {\textbf{IT Infra Automation Monitoring using GenAI} $|$ \emph{CI/CD, GCP, Github Action, FastAPI}}{January 2024}
%       \resumeItemListStart
%         \resumeItem{Wrote a general Message Queue consumer API simulating different error scenarios.}
%         \resumeItem{CI/CD setup: Faced with insufficient GCE permissions, I built a CI server that integrates with GitHub Actions.}
%         \resumeItem{Utilize IAM, Cloud Run, GCE, Artifact Registry and Log Exporter SDK for the hackathon.}
%       \resumeItemListEnd
%       \resumeProjectHeading
%           {\textbf{iThome Ironman 30-Day Article Series} $|$ \emph{FastAPI, PostgreSQL, Redis, Docker, Pytest, MQ}}{May 2023}
%           \resumeItemListStart
%             \resumeItem{Topic : "FastAPI Implementation, Testing, and Deployment."}
%             \resumeItem{Use Redis to implement caching for pagination and 'get by id' operations, achieving a 1.5x performance boost.}
%             \resumeItem{Implement a primary-replica structure to enhance parallel reading performance by over 1.3 times.}
%             \resumeItem{Over 2500 people viewed the article series, with an average of 300 views per article.}
%           \resumeItemListEnd

%     \resumeSubHeadingListEnd


%
%-----------TECHNICAL SKILLS-----------
% \section{Technical Skills}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%      \textbf{Languages}{: C, C++, Python, Golang} \\
%      \textbf{Frameworks}{: FastAPI, Flask, Django, Gin, Apache Airflow} \\
%      \textbf{Databases}{: MySQL, PostgreSQL, Redis, SQLite } \\
%      \textbf{DevOps Tools}{: Docker, Kubernetes, Helm, Terraform, GitHub Actions, GCP, Git, Linux} \\
%      \textbf{Backend Development}{: Distributed Systems, Cloud Native, Data Engineering} \\
%     }}
%  \end{itemize}


%-------------------------------------------
\end{document}